Constraining gravitational wave amplitude birefringence with GWTC-3

### 2022-12-09 src/tex/ms.tex
Formatting

\begin{figure*}[ht]
    \script{violin_kappa.py}
    \includegraphics[width=\textwidth]{figures/violin_kappa.pdf}
    \caption{
        The violin plot shows the posterior of $\kappa$ for 69 events in this study.
        Each violin represents a different event.
        The color of the violins represents the quotient of the median and standard deviation of the posterior.
        The orange horizontal solid line represents the median of $\kappa$, and the orange dashed lines enclose the $90\%$ confidence interval.
        The yellow horizontal solid line represents $\kappa=0$.
    }
    \label{fig:violin_kappa}
\end{figure*}

@@

\subsection{Constaint on $\kappa$}
% Constraint on $\kappa$
In figure \ref{fig:posterior_kappa}, we show both the restricted posterior of $\kappa$ and the generic posterior of $\kappa$.
The restricted posterior of $\kappa$ is calculated by equation \ref{eq:restricted_posterior} with the assumption that $\kappa$ is a single value constant.
The generic posterior of $\kappa$ is calculated by equation \ref{eq:generic_posterior} with the assumption that $\kappa$ is a true value drawn from a Gaussian distribution.
The median of the restricted posterior of $\kappa$ within $90\%$ confidence interval is \variable{output/restricted_kappa_median.txt}.
The median of the generic posterior of $\kappa$ within $90\%$ confidence interval is \variable{output/generic_kappa_median.txt}.
Note that the result is consistent with GR when $\kappa=0$.

@@

\pagebreak
\bibliography{bib}

>>>>

\begin{figure*}[ht]
    \script{violin_kappa.py}
    \includegraphics[width=\textwidth]{figures/violin_kappa.pdf}
    \caption{
        The violin plot shows the posterior of $\kappa$ for 69 events in this study.
        Each violin represents a different event.
        The color of the violins represents the quotient of the median and standard deviation of the posterior.
        The blue horizontal solid line represents the median of $\kappa$, and the blue dashed lines enclose the $90\%$ confidence interval.
        The pink horizontal solid line represents $\kappa=0$.
    }
    \label{fig:violin_kappa}
\end{figure*}

@@

\subsection{Constaint on $\kappa$}
% Constraint on $\kappa$
In figure \ref{fig:posterior_kappa}, we show both the restricted posterior of $\kappa$ and the generic posterior of $\kappa$.
The restricted posterior is calculated by equation \ref{eq:restricted_posterior} with the assumption that $\kappa$ is a single value constant.
The generic posterior is calculated by equation \ref{eq:generic_posterior} with the assumption that $\kappa$ is a true value drawn from a Gaussian distribution.
The median of the restricted posterior within $90\%$ confidence interval is \variable{output/restricted_kappa_median.txt}.
The median of the generic posterior within $90\%$ confidence interval is \variable{output/generic_kappa_median.txt}.
Note that the result is consistent with GR when $\kappa=0$.

@@

% \pagebreak
\bibliography{bib}
